---
title: "Cross Validation"
output: github_document
---

```{r setup_and_data_visualization_preferences}
library(tidyverse)
library(patchwork)
library(stringr)
library(p8105.datasets)
library(mgcv)
library(gam)
library(modelr)
library(broom)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

What to get out of this:

1) How to use prediction accuracy to compare models of varying degrees of complexity using cross-validation

2) Need to build models of varying degrees of complexity using various tools. Less important to understand specific tools.

## Simulate data

Identify how to choose right model

```{r}
nonlin_df =
  tibble(
    id = 1:100,
    x = runif(100, 0, 1),
    y = 1 - 10 * (x - 0.3) ^ 2 + rnorm(100, 0, 0.3)
  )
```

Look at data

```{r}
nonlin_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point()
```

## Cross validation -- by hand

Get training and testing datasets

```{r}
train_df = sample_n(nonlin_df, size = 80)
test_df = anti_join(nonlin_df, train_df, by = "id")
```

This creates two df's that do not overlap. Samples train 80/100, and then test for the remaining 20

Fit three models.

```{r}
linear_mod = lm(y ~ x, data = train_df)
smooth_mod = mgcv::gam(y ~ s(x), data = train_df)
wiggly_mod = mgcv::gam(y ~ s(x, k = 30), sp = 10e-6, data = train_df)
```

Can I see what I just did

```{r}
train_df %>% 
  add_predictions(linear_mod) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() + 
  geom_line(aes(y = pred), color = "red")

train_df %>% 
  add_predictions(smooth_mod) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() + 
  geom_line(aes(y = pred), color = "red")

train_df %>% 
  add_predictions(wiggly_mod) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() + 
  geom_line(aes(y = pred), color = "red")

train_df %>% 
  gather_predictions(linear_mod, smooth_mod, wiggly_mod) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() + 
  geom_line(aes(y = pred), color = "red") + 
  facet_grid(. ~ model)
```

Smooth model probably should do best.

gather_predictions to look at multiple models at once

Look at prediction accuracy: look at root mean square error using the linear model on TESTING dataset

```{r}
rmse(linear_mod, test_df)
rmse(smooth_mod, test_df)
rmse(wiggly_mod, test_df)
```

We want the lowest RMSE.




