---
title: "Linear Models"
date: "11/26/2020"
output: github_document
---

```{r setup_and_data_visualization_preferences}
library(tidyverse)
library(patchwork)
library(stringr)
library(p8105.datasets)


knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Data import and tidying

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood
  ) %>% 
  filter(borough != "Staten Island") %>% 
  select(price, stars, borough, neighborhood, room_type)
```

## Fit a model

Want to know how price of rental is related to stars and borough

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price, color = borough)) + 
  geom_point()
```

Want to fit a model to this

```{r}
price_fit = lm(price ~ stars + borough, data = nyc_airbnb)
```

Lets look at model results generically

```{r in}
price_fit

#This gives a fair bit of info
summary(price_fit)

#This one give t statistic and p-value for each individual coefficient
summary(price_fit)$coef
```

```{r include = FALSE}
#These outputs do not seem useful
coef(price_fit)
fitted.values(price_fit)
residuals(price_fit)
```


Tidy results of fit

```{r}
broom::glance(price_fit)

broom::tidy(price_fit)
```

For every one-unit increase in stars, price of room increases by $32 keeping borough fixed.
Implicitly ref group is Bronx (first alphabetical). Room in Manhattan is $90 more than in Bronx.

Get test stat for each and p-value

Queens is not statistically significant

```{r}
broom::tidy(price_fit) %>% 
  select(-std.error, -statistic) %>% 
  mutate(
    term = str_replace(term, "borough", "Borough: ")
  ) %>% 
  knitr::kable()
```

